Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-10 paper/disc20clustering.tex
Expanding and rewriting the proof of k=3

\begin{proof}
	If no component respecting partition exists after the merge of components, \TAlg simply ends the phase and performs no reconfiguration.
	It suffices to show that the merged component has size at least $4$ to conclude that \TAlg incurs no cost.

@@

	Now we lower-bound the cost of $\OPT$.
	By $\OPT(\sigma_I)$ and $\OPT(\sigma_E)$ we denote the cost of $\OPT$ on requests from sequences $\sigma_I$ and $\sigma_E$, respectively.
	Note that these costs are defined with respect to components of \TAlg in this phase.
	By $\OPT(M)$ we denote the cost of migrations performed by $\OPT$ in this phase.

>>>>

\begin{proof}
	If no component respecting partition exists after the merge of components, then \TAlg resets all components, ends the phase and performs no reconfiguration.
	It suffices to show that the merged component has size at least $4$ to conclude that \TAlg incurs no cost.

@@

	Now we lower-bound the cost of the optimal offline solution.
	To this end, we fix any optimal offline algorithm $\OPT$.
	By $\OPT(\sigma_I)$ and $\OPT(\sigma_E)$ we denote the cost of $\OPT$ on requests from sequences $\sigma_I$ and $\sigma_E$, respectively.
	Note that these costs are defined with respect to components of \TAlg in this phase.
	By $\OPT(M)$ we denote the cost of migrations performed by $\OPT$ in this phase.
